
---
title: "Chapter 5"
output:
  rmarkdown::github_document
---

#1-a)

Plugging in to the cdf of rayleigh F,
F(3)-F(1) should be the answer


```{r}
(1-exp(-9/2))-(1-exp(-1/2))
```

#1-b)

If F(x)=1/j, whats x?

or $F^{-1}(1/j)=?$


q1=sqrt(-2*log(1-1/4)) 

```{r}
sqrt(-2*log(1-1/4))
```

q2=sqrt(-2*log(1-2/4))

```{r}
sqrt(-2*log(1-2/4))
```

q3=sqrt(-2*log(1-3/4)) 

```{r}
sqrt(-2*log(1-3/4))
```

#2-a)

for x in (0,0.25) f(x)=2
this gives 1/2 probability mass

for x in (0.25,1) f(x)=2/3
this also gives 1/2 probability mass since (3/4)*(2/3)=0.5

#2-b)

if its bigger than 1 it will make integral>1 
which is not allowed


#3-a)
To be a valid pdf
it must be >0
and integrate to 1

since f and F are >0 g is also >0
since $F^{2}$ is the antiderivative of $Ff$

$F^{2}|^{\infty}_{-\infty}$=1-0=1

#3-b)
h is positive since f(-x) and f(x) are positive.

It integrates to 1 because for the second term of the sum the integral is 1/2.

And for the first term
if we substitute -x=u then -dx=du
we get the same integral with limits reversed.

u going from 
positive infinity to negative. The answer comes out negative. But we have a minus sign from -dx

So its 1/2


#4-a)

P(X<=x|X>a)= P(a<X<=x)/P(X>a)

P(a<X<=x)=F(x)-F(a)
P(X>a)=1-F(a)

#4-b)
derivative of above is
f(x)/(1-F(a))

#4-c)
1-F(a) is >0 and f is >0, so its >0
it integrates to 1 because
the the limit of integration is from a to infinity
which gives 1-F(a) which cancels.


#5-a)
$A=\pi R^2$

$E(A)=\pi E(R^2)=\pi(1/3)$

$Var(A)=Var(\pi R^2)=\pi^2 Var(R^2)$

$Var(R^2)=E(R^4)-E^2(R^2)$

$E(R^4)$ is integral from 0 to 1 of $R^4$
which is 1/5

and $E(R^2)^2=(1/3)^2$

so the answer is 1/5-1/9

#5-b)
$P(\pi R^2 \le a)=P(R \le \sqrt{a/\pi})=\sqrt{a/\pi}$

for $0< a< \pi$, because R is Unif(0,1)

for $\pi\le a$ its 1

for $a\le 0$ its 0

Differentiating wrt to a gives the pdf.


#6-a)

For $X \sim Unif(0,1), \mu=1/2, \sigma=\frac{1}{\sqrt(12)}$

So 

$P(\mu-\sigma<X<\mu+\sigma)$ = length of that interval


For 1 std => 2/sqrt(12)

For 2 std => 4/sqrt(12)

For 3 std => 6/sqrt(12)


#6-b)

For $X \sim Expo(1)$ 

$E(X)=1$ 

$\sigma=1$

$P(\mu-\sigma<X<\mu+\sigma)$ 

For 1 std $P(0<X<2)$

plugging in to its cdf, $1-e^{-2}$

For 2 std $P(0<X<3)$ its $1-e^{-3}$

For 3 std $P(0<X<4)$ its $1-e^{-4}$


#6-c)

For $X \sim Expo(1/2)$ 

$E(X)=2$

$\sigma=2$

For 1 std $P(0<X<4)$ its $1-e^{-2}$

For 2 std $P(0<X<6)$ its $1-e^{-3}$

For 3 std $P(0<X<8)$ its $1-e^{-4}$

Same as above, since lambdas cancel.

This is true for any expo.

#7-a)

F is increasing, right cont and converges to 0 and 1 for -infinity, +infinity (ie 0 and 1)

its pdf is 

https://www.wolframalpha.com/input/?i=derivative+(2%2Fpi)*sin%5E-1(sqrt(x))

for 0<x<1

#7-b)
its positive and integrates to 1

#8-a)
https://www.wolframalpha.com/input/?i=integral+12x%5E2(1-x)

for 0<x<1

#8-b)
https://www.wolframalpha.com/input/?i=integral+12x%5E2(1-x)+from+0+to+1%2F2

#8-c)
Mean

https://www.wolframalpha.com/input/?i=integral+12x%5E3(1-x)+from+0+to+1

which is 0.6

E(X^2)
https://www.wolframalpha.com/input/?i=integral+12x%5E4(1-x)+from+0+to+1

which is 0.4
0.4-(0.6)^2=0.04

#9)

1st quadrant in 

https://www.wolframalpha.com/input/?i=integral+1%2F(pi*(1%2Bx%5E2))


#10-a)

1/8 is the pdf

and (2-0)+(7-3)= 2+4=6
answer is 6/8

#10-b)

P(U<=x | U is in (3,7))

is 

P(U<=x,3<U<7)/P(3<U<7)=((x-3)/8)/(4/8) = (x-3)/4


#11-a)













