#1)

$$P(U\le ?)=1/2$$

$$F^{-1}(1/2)=?$$


cdf of U is 

$$\frac {x-a}{b-a}$$

So if


$$
  y=\frac {x-a}{b-a}
$$

$$
  y(b-a)+a=x
$$

$$
  F^{-1}(x)=x(b-a)+a
$$

$$
  F^{-1}(1/2)=(b+a)/2
$$


Mode of U is every point between a and b.


#2)

cdf of X is F(x) is

$$
  1-e^{-\lambda x}
$$
Find the inverse

$$
  \begin{aligned}
    y&=1-e^{-\lambda x}\\
    e^{-\lambda x}&=1-y\\
    -\lambda x&=log(1-y)\\
    x&=-\frac{log(1-y)}{\lambda}
  \end{aligned}
$$
So

$$ F^{-1}(1/2) = -\frac{log(1/2)}{\lambda} $$

Since mode is the value that maximizes the pdf, and the pdf is a decreasing function, its max is at 0

$$
  \begin{align}
  f(x)&=\lambda e^{-\lambda x}\\
  f(0)&=\lambda
  \end{align}
$$

#3)

integrate to find the cdf

$$
  \begin{align}
  \int_1^t ax^{-(a+1)}&=-x^{-a}\Big|_1^t \\
  &=-t^{-a}--1\\
  &=1-t^{-a}
  \end{align}
$$
find the inverse

$$
  \begin{align}
    1-t^{-a}&=y\\
    1-y&=t^{-a}\\
    (1-y)^{-1/a}&=t
  \end{align}
$$

Set y=1/2, so the median is

$$
  (1/2)^{-1/a}
$$

The pdf is a decreasing function.
For example the curve for a=2 looks like this.
So the max is at x=1, ie. mode is a

```{r, echo=TRUE}
curve(2/(x^3), from=1, to=10, 100)
```

#4)

```{r, echo=TRUE, eval=TRUE, cache=TRUE}
plot(0:5,dbinom(0:5,5,1/3))

which.max(pbinom(0:5,5,1/3)>=0.5)-1

which.max(dbinom(0:5,5,1/3))-1
```

Then middle of 1 and 2 is the median
and 1,2 are the modes

```{r, echo=TRUE, eval=TRUE, cache=TRUE}
plot(0:6,dbinom(0:6,6,1/3))

which.max(pbinom(0:6,6,1/3)>=0.5)-1

which.max(dbinom(0:6,6,1/3))-1
```

Here all are the same

#5)
if n is odd (n+1)/2 is the median, all are modes

if n is even n/2 and (n/2)+1 medians (or by convention the middle of those), all are modes


#6)

```{r, eval=TRUE}
#A mostly non rainy year

rain<-rep(0,365)
days<-sample(1:365,10)
amounts<-sample(1:10,10)
rain[days]<-amounts

mean(rain)
median(rain)
max(rain)


mean(rain[rain>0])
median(rain[rain>0])
max(rain[rain>0])
```

#7)

beta with a=4, b=3

```{r, echo=TRUE}
  curve(x^3*(1-x)^2, from=0, to=1, 100)
```

$$
  \begin{align}
  \frac{d}{dx}x^{a-1}(1-x)^{b-1}&=(a-1)x^{a-2}(1-x)^{b-1}-x^{a-1}(b-1)(1-x)^{b-2}\\
  &=0\\
  \end{align}
$$

gives

$$
  x=(a-1)/(a+b-2)
$$

#8)

Notice that it says proportional, so beta a=3, b=1 is
$$
  kx^2
$$

antiderivative is $kx^3/3$

this should integrate to 1 from 0 to 1, so k=3

inverse of that is $(x)^{1/3}$

plug in 1/2

```{r, eval=TRUE}
(1/2)^(1/3)
```

```{r, echo=TRUE}
  curve(x^2*(1-x)^0, from=0, to=1, 100)
```
