#1)

$$P(U\le ?)=1/2$$

$$F^{-1}(1/2)=?$$


cdf of U is 

$$\frac {x-a}{b-a}$$

So if


$$
  y=\frac {x-a}{b-a}
$$

$$
  y(b-a)+a=x
$$

$$
  F^{-1}(x)=x(b-a)+a
$$

$$
  F^{-1}(1/2)=(b+a)/2
$$


Mode of U is every point between a and b.


#2)

cdf of X is F(x) is

$$
  1-e^{-\lambda x}
$$
Find the inverse

$$
  \begin{aligned}
    y&=1-e^{-\lambda x}\\
    e^{-\lambda x}&=1-y\\
    -\lambda x&=log(1-y)\\
    x&=-\frac{log(1-y)}{\lambda}
  \end{aligned}
$$
So

$$ F^{-1}(1/2) = -\frac{log(1/2)}{\lambda} $$

Since mode is the value that maximizes the pdf, and the pdf is a decreasing function, its max is at 0

$$
  \begin{align}
  f(x)&=\lambda e^{-\lambda x}\\
  f(0)&=\lambda
  \end{align}
$$

#3)

integrate to find the cdf

$$
  \begin{align}
  \int_1^t ax^{-(a+1)}&=-x^{-a}\Big|_1^t \\
  &=-t^{-a}--1\\
  &=1-t^{-a}
  \end{align}
$$
find the inverse

$$
  \begin{align}
    1-t^{-a}&=y\\
    1-y&=t^{-a}\\
    (1-y)^{-1/a}&=t
  \end{align}
$$

Set y=1/2, so the median is

$$
  (1/2)^{-1/a}
$$

The pdf is a decreasing function.
For example the curve for a=2 looks like this.
So the max is at x=1, ie. mode is a

```{r, echo=TRUE}
curve(2/(x^3), from=1, to=10, 100)
```

#4)

```{r, echo=TRUE, eval=TRUE, cache=TRUE}
plot(0:5,dbinom(0:5,5,1/3))

which.max(pbinom(0:5,5,1/3)>=0.5)-1

which.max(dbinom(0:5,5,1/3))-1
```

Then middle of 1 and 2 is the median
and 1,2 are the modes

```{r, echo=TRUE, eval=TRUE, cache=TRUE}
plot(0:6,dbinom(0:6,6,1/3))

which.max(pbinom(0:6,6,1/3)>=0.5)-1

which.max(dbinom(0:6,6,1/3))-1
```

Here all are the same

#5)
if n is odd (n+1)/2 is the median, all are modes

if n is even n/2 and (n/2)+1 medians (or by convention the middle of those), all are modes


#6)

```{r, eval=TRUE}
#A mostly non rainy year

rain<-rep(0,365)
days<-sample(1:365,10)
amounts<-sample(1:10,10)
rain[days]<-amounts

mean(rain)
median(rain)
max(rain)


mean(rain[rain>0])
median(rain[rain>0])
max(rain[rain>0])
```

#7)

beta with a=4, b=3

```{r, echo=TRUE}
  curve(x^3*(1-x)^2, from=0, to=1, 100)
```

$$
  \begin{align}
  \frac{d}{dx}x^{a-1}(1-x)^{b-1}&=(a-1)x^{a-2}(1-x)^{b-1}-x^{a-1}(b-1)(1-x)^{b-2}\\
  &=0\\
  \end{align}
$$

gives

$$
  x=(a-1)/(a+b-2)
$$

#8)

Notice that it says proportional, so beta a=3, b=1 is
$$
  kx^2
$$

antiderivative is $kx^3/3$

this should integrate to 1 from 0 to 1, so k=3

inverse of that is $(x)^{1/3}$

plug in 1/2

```{r, eval=TRUE}
(1/2)^(1/3)
```

```{r, echo=TRUE}
  curve(x^2*(1-x)^0, from=0, to=1, 100)
```

#9-a)
To find the cdf of log normal,

compute
$$
  
  P(Y\le k)=P(e^X\le k)=P(X\le log(k))=F(log(k))
$$
where F is the cdf of X

So when is $F(log(k))=1/2$
when $logk=\mu$
or when $k= e^{\mu}$

so Student A is correct

for example

```{r, echo=TRUE}
x<-exp(rnorm(1000000,2,2))
median(x)-exp(2)
```



#9-b)
To find the pdf take the derivative of the above.

We get 

$$
  f(log(k))/k
$$

where f is the pdf of normal.

To find the maximum:

```{r, echo=TRUE}
h<-function(k) dnorm(log(k))/k
optimize (h,lower=0, upper=1,maximum = TRUE)
```


```{r}
curve(dnorm(log(x))/x,from=0.01, to=1, 1000)
```

So Student B is not correct

#9-c)

Nope


#10) TODO

#11-a)

Skew of $Z_j$ is the skew of $X_j$ because

$$
  \begin{align}
  E(\frac{Z_j-\mu_{Z_j}}{\sigma_{Z_j}})^3&=E(\frac{Z_j-0}{1})^3\\
  &=E(Z_j)^3\\
  &=E(\frac{X_j-\mu}{\sigma})^3
  \end{align}
$$

Skew of $\bar{Z_n}$ is

$$
E(\frac{\bar{Z_n}-\mu_{\bar{z_n}}}{\sigma_{\bar{z_n}}})^3
$$

$\mu_{\bar{z_n}}=E(\bar{Z_n})$ is the mean of the sample mean of the standardized X, which equals 0 because the sample mean is unbiased

$\sigma_{\bar{z_n}}=\sqrt{Var(\bar{Z_n})}=\sqrt{\frac{1^2}{n}}=\sqrt{1/n}$

and

$\bar{Z_n}=\frac{1}{n}\sum_{j=1}^{n}Z_j=\frac{1}{n}\sum_{j=1}^{n}\frac{X_j-\mu}{\sigma}$

putting those in place we get

$$
E(\frac{(\frac{1}{n}\sum_{j=1}^{n}\frac{X_j-\mu}{\sigma})-0}{\sqrt{1/n}})^3=E(\frac{\sqrt{n}}{\sigma}\sum_{j=1}^{n}\frac{X_j-\mu}{n})^3=E(\frac{\sqrt{n}}{\sigma}(\bar{X_n}-\mu))^3=E(\frac{\bar{X_n}-\mu_{\bar{x_n}}}{\sigma_{\bar{x_n}}})^3
$$

But that is the skew of $\bar{X_n}$

#11-b)

we are assuming Xs have mean 0 and sd 1

And need to compute skewnewss of the random variable $\bar{X_n}$

ie. 
$$
E(\frac{\bar{X_n}-\mu_{\bar{x_n}}}{\sigma_{\bar{x_n}}})^3
$$
$\mu_{\bar{x_n}}=0$

${\sigma_{\bar{x_n}}}=\sqrt{\frac{\sigma^2}{n}}=\sqrt{\frac{1}{n}}$

So

$$
E(\frac{\bar{X_n}-\mu_{\bar{x_n}}}{\sigma_{\bar{x_n}}})^3=E(\bar{X_n}\sqrt{n})^3=n^{3/2}E(\bar{X_n})^3=n^{3/2}E(\frac{\sum_{j=1}^{n}X_j}{n})^3=n^{3/2}\cdot n^{1/3}E(\sum_{j=1}^{n}X_j)^3
$$

Using the hint, when expanded, the expectation in the last expression contains only the stated terms cubes of an $X_j$ or products of three $X_i$ where at least one of them is different

By theorem 7.3.2, expectation of the product of independent rvs are the product of the expectations. So only the cubes come out as non-zero, expectation of terms for the the other kind are 0.

#11-c)

When n is large this says skewness of the sample mean is 0.